  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry} % Document margins
\usepackage{hyperref}

\name{Devin McGloin}
\address{909~$\cdot$~801~$\cdot$~4429 \\ \href{mailto:devin@devinmcgloin.com}{devin@devinmcgloin.com}}
\address{\href{https://devinmcgloin.com}{devinmcgloin.com} \\ \href{https://github.com/devinmcgloin}{github.com/devinmcgloin}}

\begin{document}


%----------------------------------------------------------------------------------------
%	ABOUT SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Profile}

%\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf New York University} \hfill  May 2017 \\
BS Computer Science \hfill {\em New York, NY}
\end{rSection}

%----------------------------------------------------------------------------------------
%	CURRENT PROJECTS  SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}


\begin{rSubsection}{Fokal}{June 2016 - Present}{\href{https://fok.al}{fok.al}}{API Design, Golang, Web design}
\item Designed hypermedia API for image uploading, tagging and various other social graph operations.
\item Implemented API spec from the ground up using Go, PostgreSQL and Redis with an extensible permission model.
\item Integrated with various computer vision and geo-location services in order make better use of image metadata.
\item Designed and implemented mobile first web interface to API functionality using React, ES6 and Webpack.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Advent}{May 2015 - June 2016}{\href{https://devinmcgloin.com/advent}{devinmcgloin.com/advent}}{Webservices, HTTP, Cloud Computing}
\item Created Advent, a port of the classic terminal game Collosal Cave Adventure to Facebook Messenger and Telegram.
\item Developed a wrapper of the \href{https://smooch.io}{smooch.io} messaging API and released it under the MIT License.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{AIR}{November 2014 - December 2015}{\href{https://devinmcgloin.com/AIR}{devinmcgloin.com/air}}{Knowledge Representation, API design, Performance Profiling}
\item Designed AIR, a knowledge representation system that models actions and content in the world.
\item Implemented a simple prototype of the system that handles plurality, ownership, inheritance and type classes.
% \item Developed 
\end{rSubsection}
\end{rSection}

%------------------------------------------------

\begin{rSection}{Experience \& Awards}

\begin{rSubsection}{Union Realtime}{August 2016 - December 2016}{Intern}{New York, NY}
% \item Developed anomily detection systems for timeseries data sets.
% \item Created means for inspecting the validity of individual datums across the entire database.
\item Took ownership and refactored core code base for simpler extensibility and better error detection.
\item Investigated and resolved data integrity errors, resulting in more accurate data for clients.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{REI}{November 2013 - Dec 2015}{Salesperson}{New York, NY}
\item Assisted customers with technical expertise regarding an array of outdoor products.
\end{rSubsection}

\begin{rSubsection}{Classic Car Club Manahattan}{September 2013 - May 2104}{Intern}{New York, NY}
\item Learned the foundations of system troubleshooting, preventative maintenance as well as organizing a shop overhaul.

\end{rSubsection}
%------------------------------------------------

\begin{rSubsection}{Boy Scouts of America}{October 2009 - May 2013}{Eagle Scout}{Redlands, CA}
\item Organized and completed a service project consisting of over 600 volunteer hours and donations of \$4,000.
%\item Procured donations from private and corporate  donors including Esri, Home Depot, Hines and Scotts.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}{(In order of fluency)}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Go, Python, C, Java, Latex, Racket, Haskell\\
Tools & Linux, Git, Vim, Maven\\
Services & AWS, Heroku, GitHub, Travis CI\\
Databases & MySQL, PostgreSQL, Redis, ElasticSearch\\
\end{tabular}

\end{rSection}



\begin{rSection}{Interests}

Programming Languages, Backpacking, Photography, Design, Visited 35 US States \& 6 Canadian Provinces

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}

